---
title: "My example Software Carpentry"
author: "PJM"
date: "July 7, 2015"
output: word_document
---

Some text like this, some of it is **bold** Some might be *italic*

- first line
- second line
- third line




1. numbered bullets 1
2. numbered bullets 2
3. numbered bullets 3


#A section

How are you?

##A sub section

I am fine, i hope everything is going well

#A new section

I will go to Spain during August


Create a [web link](http://google.com)

Link to an image

```{r load_stuff, echo=FALSE}
library(ggplot2)

df <- read.csv('/Users/PJ/Downloads/gapminder-FiveYearData.csv')


```
```{r first_chunck}


ggplot(data = df, aes(x=gdpPercap, color=continent, fill=continent)) +
  geom_density(alpha=0.5)+
  scale_x_log10()+
  facet_wrap(~year)+
  xlab("gdpPercap") + ylab("")+
  ggtitle("My GGPLOT") 


```

```{r second_chunck}

ggplot(data = df, aes(x = year, y = gdpPercap, by=country)) +
  geom_point() +
  geom_line(aes(color=continent))



```{r third_chuk, echo=FALSE, dpi=30}
library(ggplot2)



df <- read.csv('/Users/PJ/Downloads/gapminder-FiveYearData.csv')

ggplot(data = df, aes(x=gdpPercap, color=continent, fill=continent)) +
  geom_density(alpha=0.5)+
  scale_x_log10()+
  facet_wrap(~year)+
  xlab("gdpPercap") + ylab("")+
  ggtitle("My GGPLOT")


```

The mean per capital GDP in the data set is
`r mean(df$gdpPercap)`.



